Representing Nouns as Byte Arrays

### 2025-05-29 mss.tex
Post newt

\newcommand{\authorname}{N. E. Davis}
\newcommand{\authorpatp}{\patp{lagrev-nocfep}}
\newcommand{\affiliation}{Zorp Corp}

@@

\subsection{\texttt{++jel}, the Na\"{i}ve Encoding}

@@

\subsection{\texttt{++jam}, the Practical Serialization}

@@

>>>>

\newcommand{\authorname}{N. E. Davis \& Sam Parker}
\newcommand{\authorpatp}{\patp{lagrev-nocfep} \& \patp{zod}}
\newcommand{\affiliation}{Zorp Corp \& —}

@@

\section{\texttt{++jel}, the Na\"{i}ve Encoding}

@@

\section{\texttt{++jam}, the Practical Serialization}

@@

\subsection{\texttt{newt} Encoding}

“Newt” encoding is a runtime-oriented extension of \texttt{++jam}-based noun serialization which adds a short identifying header in case of future changes to the serialization format.  A version number (currently as a single bit) precedes a serialization length followed by the \texttt{++jam} serialization of the noun.  The version number is currently always \texttt{0b0}, but this may change in the future.

\begin{lstlisting}[style=listingcode]
  V.LLLL.JJJJ.JJJJ.JJJJ.JJJJ.JJJJ.JJJJ
\end{lstlisting}

\noindent{}
where \texttt{V} is the version number, \texttt{L} is the total length of the noun in bytes, and \texttt{J} is the \texttt{++jam} serialization of the noun.

Runtime communications vanes like \texttt{\%khan} and \texttt{\%lick} utilize this encoding locally.  It is exclusively used as a Unix affordance at the current time.

\section{\texttt{+\$bulk}, the Directed Graph Encoding}

\end{document}
